%-------------------------
% Resume in Latex
% Author : Gundappa Vijayakumar
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[document]{ragged2e}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/gvijayakumar/}{\Large G VIJAYAKUMAR}} & Email : \href{mailto:vijayakumar.gundappa@gmail.com}{vijayakumar.gundappa@gmail.com}\\
  \href{https://www.linkedin.com/in/gvijayakumar}{https://www.linkedin.com/in/gvijayakumar} & Mobile : +98454 45387 \\
\end{tabular*}

%-----------SUMMARY-------------------
\section{Summary}
{\begin{justify}
Techno-functional leader with around 20 years of experience including 2 years of working at US location, in Development, DevOps, Web pen-testing, experiences in diverse IT products.  Have experience working with diverse cultures,\& countries. Organizational efficiency with proven track record of providing strategic,technical \& operational leadership to increase productivity \& production stability in Program Management, IT Delivery,IT Infrastructure Management \& Cloud Infrastructure with optimum usage of resources
\end{justify}}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Management}{Calcutta, India}
      {Executive MBA/Program for Business Managers;  }{June. 2006 -- May. 2007}
    \resumeSubheading
      {Malnad College of Engineering, Mysore University}{Hassan, India}
      {Master of Computer Applications; }{Aug. 1994 -- July. 1997}
    \resumeSubheading
      {Mysore University}{Mysore, India}
      {Post Graduate Diploma in Business Administration; }{Jan. 2009 -- Dec. 2010}  
    \resumeSubHeadingListEnd
%---------CERTIFICATION-----------------
 \section{Certification}

a.Scrum Master CSM  2015\hfill
b.RHD236 – Red Hat Linux Kernel Internals (RHEL 7.1) 2001\linebreak
c.MQ System Admin 2005 \hfill d. Websphere Admin 2005 \linebreak
e.Oracle certification on “Oracle Enterprise Manager 12c Certified Implementation Specialist” 2016
%----------Awards-----------------------
\section{Awards}
\begin{itemize}\setlength{\itemsep}{0pt}
\item Received Active Advisor Award 2016, An award given across Fidelity's global locations for proactive advising business users on infrastructure 
\item Received an Award \& a Letter of Appreciation in 2015 from Vice President on successful completion of application migration from AIX \& Solaris to Linux.
\item \begin{justify}Received an Award a Letter of Appreciation in Dec, 2016, for the successful implementation of CAWR(Centralized Automatic Workload Repository) using Oracle Enterprise Manager 12c\end{justify}
\item Received an Award \& Letter of Appreciation for contributing to the learning initiatives for FMR India as Learning Catalyst in 2010
\item Received an Award \& Letter of Appreciation from Country head for dedicated \&
enthusiastic participation in the campus hiring
\item Received an Award \& Letter of Appreciation for contributing to the learning initiatives for FMR India by being the brand ambassador for culture of coding in 2018
\end{itemize}
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Fidelity Investments}{Bangalore, India}
      {Senior Project Manager}{July 2004 - Present}
      \resumeItemListStart
        \resumeItem{Bigdata Devops}
          {\begin{justify}Managing, supporting \& developing automation for Hadoop big data eco system, mainly developing Enterprise Message/data Bus As A Managed Service using Apache Kafka. The development involves designing , developing cloud based Message Bus PAAS solution using openstack , ansible, node.jS,grafana,prometheus with continuous integration/deployment using git stash, jenkins. This project has saved 1 million dollars in capex and 1.5 million from vendor support as we used pure open source vanilla products. This project has potential to save 20-30\% of cost over physical environment, with exponential increase in time to market (from months to minutes)\linebreak\linebreak
          \end{justify}}
        \resumeItem{Data engineering team}
         {\begin{justify}Responsible for managing database related projects. An in house application for managing the databases :Database Administration Tool. Oracle Enterprise Manager institutionalization. Reducing the number of duplicate enterprise infrastructure applications by decommissioning legacy ones, saved millions of dollars by optimizing the usage \& decommissioning two legacy applications namely Database Administration Tool \& Database Enterprise Audit System. Reducing the number of duplicate enterprise infrastructure applications by decommissioning legacy ones, saved 3.5 million dollars by optimizing the usage \& decommissioning two legacy applications/teams namely Database Administration Tool (DAT)\& Database Enterprise Audit System(DEAudit)
         \end{justify}}
         \resumeItem{Distributed Hosting Application Operations \& Engineering, Release engineering}
         {\begin{justify}In this role I was responsible for managing more than 40 member teams, teams consists of 
         \begin{itemize}    
        \item[-]Middleware teams, the teams that are responsible for managing, engineering,supporting middle products like app servers, web servers, message queuing etc.,
       \item[-]Release engineering teams responsible for supporting , managing source code control systems for different business units
       \item[-]Application support team that supports the Fidelity institutional brokerage applications \& Personal,Workplace Investment applications
          \end{itemize}
          Saved 3 million dollars by team optimization \& infrastructure convergence. Developed UI enabled Application Deployment Tool (ADT)for automated application deployments, have saved 1 million dollars. Saved 10 million by adopting open source products over vendor product in 85\% of existing customer instances
          \end{justify}
         }
      \resumeItem{Onshore coordinator \& MW Application support MA \& Raleigh, US}
      {\begin{justify} Supporting the PWI(Personal \& Workplace Investment)enterprise applications. Planning \& executing the production application deployments by working with other enterprise support teams like capacity planning, unix technical support, etc.  Saved 5 million thru automation and cost optimization. \end{justify}}
      \resumeItemListEnd

    \resumeSubheading
      {IBM Software Labs}{Bangalore, India}
      {Project Lead}{Oct 1999 - July 2004}
      \resumeItemListStart
      	\resumeItem{Autonomic Computing}
          {Developing self managing products. As part of this have developed parsers for different product logs.}
        \resumeItem{IBM JVM Development }
          { As JPDA component owner, was responsible for architecture, designing \& validating the critical line-items that get into the IBM SDK . Implementing new JVM feature enhancements. I helped with the design, code reviews \& committing of the code for JPDA component.}
         \resumeItem{IBM JVM L3 Support}
         {Providing support to all customers using IBM JVM. Like all Websphere customers }
      \resumeItemListEnd
    

  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
